---
title: DANL Project
subtitle: "Goalies"
author: 
  - Abby Hofschnieder
  - Greta Recktenwald
  - Ayden Currier


toc: true
toc-title: "Table of Contents"
toc-depth: 2
number-sections: true

fig-width: 9

execute:
  code-tools: true
  message: false
  warning: false

from: markdown+emoji
---
```{r setup}
#| include: false
library(tidyverse)
library(skimr)
library(ggthemes)
library(hrbrthemes)

theme_set(theme_ipsum()+
          theme(strip.background =element_rect(fill="lightgray"),
                axis.title.x = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(10,0,0,0)),
                axis.title.y = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(0,10,0,0))
                )
          )
```



# Introduction

About this project:This project is to show my understanding of data analytics and how to use R studio with the data from Goalies.csv! https://www.kaggle.com/datasets/open-source-sports/professional-hockey-database?select=Goalies.csv



# Data

```{r}
library(readxl)
Goalies <- read.csv("archive/Goalies.csv")

```


## Summary Statistics

```{r}
rmarkdown::paged_table(Goalies)
```

```{r}
skim(Goalies) %>%
  select(-n_missing)
```

Name	Goalies
Number of rows	4278
Number of columns	23
_______________________	
Column type frequency:	
character	3
numeric	20
________________________	
Group variables	None



## Visualization

What Five players have the most goals scored against?



```{r}
library(dplyr)
top_5_goalies <- Goalies %>%
  arrange(desc(PostGA)) %>%
  head(5)

specific_goalies1 <- c("hrudeke01", "bannemu01", "daleyjo01", "hextaro01", 
                       "fleurma01")
top_5_data <- subset(Goalies, playerID %in% specific_goalies1)


ggplot(top_5_data, aes(x = playerID, fill = PostGA)) +
  geom_bar()
```

The player with playerID “bannemu01” showed the highest number of goals scored against

What five players have the most postseason wins?

```{r}
top_5_goalies_wins <- Goalies %>%
  arrange(desc(PostW)) %>%
  head(5)
print(top_5_goalies_wins)
```
```{r}
specific_goalies2 <- c("barrato01", "belfoed01", "brodema01", "fleurma01", 
                       "fuhrgr01")
top_5_data2 <- subset(Goalies, playerID %in% specific_goalies2)


ggplot(top_5_data2, aes(x = playerID, fill = PostW)) +
  geom_bar()
```
The player with playerID “barrato01” showed the highest number of postseason wins

What is the relationship between goalie shutouts and wins?

```{r}
library(ggplot2)
ggplot(data = Goalies) +
  geom_point(mapping = aes(x = SHO, y = W))
```

There is a positive relationship between goalie shutouts and wins. So, if a goalie continues to have shutouts, the teams chances of wining increase signifitcantly