---
title: DANL Project
subtitle: "Goalies"
author: 
  - Abby Hofschnieder
  - Greta Recktenwald
  - Ayden Currier


toc: true
toc-title: "Table of Contents"
toc-depth: 2
number-sections: true

fig-width: 9

execute:
  code-tools: true
  message: false
  warning: false

from: markdown+emoji
---
```{r setup}
#| include: false
library(tidyverse)
library(skimr)
library(ggthemes)
library(hrbrthemes)

theme_set(theme_ipsum()+
          theme(strip.background =element_rect(fill="lightgray"),
                axis.title.x = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(10,0,0,0)),
                axis.title.y = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(0,10,0,0))
                )
          )
```



# Introduction

About this project:This project is to show my understanding of data analytics and how to use R studio with the data from Goalies.csv! https://www.kaggle.com/datasets/open-source-sports/professional-hockey-database?select=Goalies.csv



# Data

```{r}
library(readxl)
Goalies <- read.csv("archive/Goalies.csv")

```


## Summary Statistics

```{r}
rmarkdown::paged_table(Goalies)
```

```{r}
skim(Goalies) %>%
  select(-n_missing)
```

Name	Goalies
Number of rows	4278
Number of columns	23
_______________________	
Column type frequency:	
character	3
numeric	20
________________________	
Group variables	None



## MPG and a Type of Cars
The following boxplot shows how the distribution of highway MPG (`hwy`) varies by a type of cars (`class`) :blue_car: :truck: :minibus:.


```{r}
ggplot(data = mpg) +
  geom_boxplot(aes(x = class, y = hwy, fill = class),
               show.legend = F) +
  labs(x = "Class", y = "Highway\nMPG") 
```


